Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/evaluation.tex
force page size

$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about topology, whereas \sysname propagated these advertisements; and

>>>>

$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements; and

### 2016-01-29 paper/related.tex
intro and labels to sections
more edits. bring back conclusion
more ediiiiiiiitsssss
force page size

\section{Related Work}

%\begin{itemize}
%	\item Regular path queries
%	\item Lots of background on BGP
%	\item Feamster rcc stuff
%	\item Logic programming BGP configs
%\end{itemize}

\dpw{We could also consider citing Boon's stuff on declarative routing.}

Our work builds on three themes of prior work.

\paragraph*{SDN Programming Languages}
\sysname{} was heavily influenced by recent SDN programming
languages such as Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
NetKAT~\cite{netkat}, as well as path queries~\cite{queries}.
Each of these languages is oriented around regular expressions, which
describe paths through a network, and predicates, which classify packets.
In particular, FatTire allows programmers to define sets of paths together
with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
and the compiler will generate appropriate
OpenFlow rules.  \sysname is more
expressive as it allows users to specify preferences among
paths and it automatically generates distributed
implementations that tolerate
any number of faults.  Because FatTire generates data plane rules up front,
before faults occur, specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch
memory.  In contrast, \sysname uses traditional distributed
control plane mechanisms to react to faults, which do not impose 
additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN.  Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike any existing SDN language.

>>>>

\section{Related Work}
\label{sec:related}

\paragraph*{SDN Languages}
\sysname{} was heavily influenced by recent SDN programming
languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire}, 
as well as path queries~\cite{queries}.
Each of these languages is oriented around regular expressions, which
describe paths through a network, and predicates, which classify packets.
In particular, FatTire allows programmers to define sets of paths together
with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
and the compiler will generate appropriate
OpenFlow rules.  \sysname is more
expressive as it allows users to specify preferences among
paths and it automatically generates distributed
implementations that tolerate
any number of faults.  Because FatTire generates data plane rules up front,
before faults occur, specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch
memory.  In contrast, \sysname uses traditional distributed
control plane mechanisms to react to faults, which do not impose
additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN.  Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike any existing SDN language.
